Attribute fusion in a latent process model for time series of graphs

### 2011-04-21 ssp2011.tex
ssp 2011 graph invariants

>>>>

\section{Change-point detection}
\subsection{Graphs Invariants}
In this paper we consider the problem of detecting chatter anomalies
in time series of graphs using attributed invariants. The particular
invariants of interests are the size, max degree, scan, and number of
triangles. Specifically, we consider linear attribute fusion with
parameter $\lambda \in \mathbb{R}^{K}_{\geq 0}$ via
  \label{eq:6}
  \mathrm{size}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
  \mathbf{1}\{ \phi(uv,t) = k \} \\
  \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
  \sum_{u \in N(v)}{\mathbf{1}\{\phi(uv,t) = k\}} \\
  \mathrm{scan}_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K}
  \lambda_k \sum_{u,w \in N(v)} \mathbf{1}\{\phi(uw,t) = k\} \\
  \label{eq:3}
  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{(u,v,w) \in
    \binom{V}{3}} h_k(u,v,w)
where $h_k(u,v,w)$ is the indicator function that the argument, a set
of three vertices, forms a triangle (3-clique) of type $k$. A triangle
is of type $k$ provided that all edges in the triangle have attribute
$k$. \\ \\
\noindent
Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6}) through
Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{m}_\lambda(t)$
of $J_{\lambda}$ based on recent past as
  \label{eq:4}
 \bar{J}^{m}_{\lambda}(t) = \frac{1}{m}\sum_{s = 1}^{m} J_{\lambda}(t - s) 
where $m \in \mathbb{N}$ specified the width of the running-average
window. The main object of our interests are then the normalized fusion
statistic $T_{\lambda}^{m}(t)$ as defined by
  \label{eq:7}
 T_{\lambda}^{m}(t) = % \begin{cases}
   % J_{\lambda}(t) - J_{\lambda}(t - 1) & \text{if $m = 1$} \\
   \frac{J_{\lambda}(t) -
     \bar{J}_{\lambda}^{m}(t)}{\sqrt{\tfrac{1}{m-1}
       \sum_{s=1}^{m}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{m}(t))^2}}
%   & \text{if $m \geq 2$}
 %  \end{cases}
for $m \geq 2$. 
\begin{theorem}
  \label{thm:1}
  Let $\lambda^{*}$ be the eigenvector corresponding to the largest
  eigenvalue of $ \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}$,
  i.e., 
   \label{eq:9}
  \lambda^{*} = \argmax_{\lambda \colon \| \lambda \| = 1}
  \lambda^{T} \mathbf{A}^{-1/2} \mathbf{B} \mathbf{A}^{-1/2}
  \lambda.
 We then have
   \label{eq:8}
 \argmax_{\lambda \in \mathcal{B}}
 \mu_{\lambda} \, \cap \, \{\lambda^{*}, - \lambda^{*}\} \not = \emptyset \\
 \argmin_{\lambda \in \mathcal{B}} \mu_{\lambda} \, \cap \, \{\lambda^{*}, -
 \lambda^{*}\} \not = \emptyset.
\end{theorem}
